### 2017-10-09 Paper/main.tex

\end{tikzpicture}
\end{center}
\captionof{figure}{Algorithmic trading process}
\label{algoproces}
\subsection{AutoRegressive Integrated Moving Average: key concepts and features}
ARIMA process are a class of univariate time series models, this kind of models attempt to predict financial variables using only information contained in their own past values and possibly current and past values of an error term.ARIMA process differ from the exponential smoothing since ARIMA focuses on the autocorrelation of the time series instead of trend and seasonality. Such model firstly proposed by Box-Jenkins %mettere riferimento
combines three factors, namely: differencing, autoregressive model and moving average model.
Where differencing is intend as the process of transformation of the timeseries such that we end up with a stationary time series which has as property no time dependency, in other terms given $X_t$ a stochastic process and $F_X(x_{t_k}+\theta$ its cumulative distribution. $X_t$ is stationary when $\forall k,\theta and t_k$ we have that:
\[ F_x(x_{t_k}_+\theta = F_x(x_{t_k} \]
aoregressive models are the ones that

>>>>

\end{tikzpicture}
\end{center}
\captionof{figure}{Algorithmic trading process}
\label{algoproces}
\subsection{AutoRegressive Integrated Moving Average: key concepts and features}
ARIMA process are a class of univariate time series models, this kind of models attempt to predict financial variables using only information contained in their own past values and possibly current and past values of an error term. ARIMA process differ from the exponential smoothing since ARIMA focuses on the autocorrelation of the time series instead of trend and seasonality. Such model firstly proposed by Box-Jenkins %mettere riferimento
combines three factors, namely: differencing, autoregressive model and moving average model.
Where differencing is intend as the process of transformation of the timeseries such that we end up with a stationary time series which has as property no time dependency, in other terms given $X_t$ a stochastic process and $F_X(x_{t_k}+\theta$ its cumulative distribution. $X_t$ is stationary when $\forall k,\theta and t_k$ we have that:
\[ F_x(x_{t_k}_+\theta = F_x(x_{t_k} \]
aoregressive models are the ones that
